---
title: "Weekday Market Patterns"
author: ""
date: ""
format: 
  html:
    theme: cosmo
    toc: true
    toc-depth: 2
    code-fold: true
    embed-resources: true
    self-contained: true
---

```{r setup, include=FALSE}
# Load core packages
suppressPackageStartupMessages({
  library(tidyverse)
  library(lubridate)
  library(plotly)
  library(DT)
  library(knitr)
})

# Try to load data packages
for(pkg in c("quantmod", "tidyquant")) {
  if(requireNamespace(pkg, quietly = TRUE)) library(pkg, character.only = TRUE)
}

# Set global options
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# Set date parameters
end_date <- Sys.Date()
start_date <- end_date - years(10)
```

```{r get-data-function}
# Function to safely get market data with multiple fallbacks
get_market_data <- function(symbol, start_date, end_date) {
  price_data <- NULL
  
  # Try quantmod first
  if(exists("getSymbols")) {
    tryCatch({
      ticker <- getSymbols(symbol, src = "yahoo", from = start_date, to = end_date, auto.assign = FALSE)
      
      if(!is.null(ticker) && nrow(ticker) > 0) {
        # Format data
        price_data <- data.frame(date = index(ticker), coredata(ticker))
        colnames(price_data) <- c("date", "open", "high", "low", "close", "volume", "adjusted")
        price_data$symbol <- symbol
        return(price_data)
      }
    }, error = function(e) NULL)
  }
  
  # Try tidyquant if available
  if(is.null(price_data) && exists("tq_get")) {
    tryCatch({
      ticker_data <- tq_get(symbol, from = start_date, to = end_date, get = "stock.prices")
      
      if(!is.null(ticker_data) && nrow(ticker_data) > 0) {
        return(ticker_data)
      }
    }, error = function(e) NULL)
  }
  
  # Try Yahoo Finance API directly
  if(is.null(price_data)) {
    tryCatch({
      # Format dates for Yahoo
      start_unix <- as.numeric(as.POSIXct(start_date))
      end_unix <- as.numeric(as.POSIXct(end_date))
      
      # Build URL
      url <- paste0(
        "https://query1.finance.yahoo.com/v7/finance/download/", 
        symbol,
        "?period1=", start_unix,
        "&period2=", end_unix,
        "&interval=1d&events=history"
      )
      
      # Download data
      temp_file <- tempfile(fileext = ".csv")
      download.file(url, temp_file, quiet = TRUE, mode = "wb")
      
      if(file.exists(temp_file) && file.info(temp_file)$size > 0) {
        data <- read.csv(temp_file, stringsAsFactors = FALSE)
        unlink(temp_file)
        
        if(nrow(data) > 0) {
          # Process data
          price_data <- data %>%
            rename_all(tolower) %>%
            mutate(date = as.Date(date), symbol = symbol)
          
          # Handle column naming differences
          if("adj.close" %in% colnames(price_data)) {
            price_data <- price_data %>% rename(adjusted = adj.close)
          } else if("adjclose" %in% colnames(price_data)) {
            price_data <- price_data %>% rename(adjusted = adjclose)
          }
          
          return(price_data)
        }
      }
      unlink(temp_file)
    }, error = function(e) NULL)
  }
  
  # Return empty data if all methods failed
  if(is.null(price_data)) {
    return(tibble(
      symbol = character(),
      date = as.Date(character()),
      close = numeric(),
      adjusted = numeric()
    ))
  }
  
  return(price_data)
}
```

```{r get-index-data}
# Define market indices by region
market_indices <- list(
  "🇺🇸 US" = c("^GSPC", "^NDX"),                                    # S&P 500, Nasdaq 100
  "🇪🇺 Europe" = c("^STOXX50E", "^FTSE", "^GDAXI", "^FCHI"),       # Euro Stoxx 50, FTSE 100, DAX, CAC 40
  "🇳🇴 Nordics" = c("^OMXSPI", "^OMXC25", "^OMXHPI", "OSEBX.OL"),  # Sweden, Denmark, Finland, Norway
  "🌏 Asia" = c("^N225", "^HSI", "000300.SS", "^KS11", "^NSEI"),    # Nikkei, Hang Seng, CSI 300, KOSPI, Nifty 50
  "🌍 Other" = c("^BVSP", "^MXX", "^GSPTSE", "^TASI", "^JN0U.JO")   # Bovespa, IPC Mexico, TSX, Tadawul, JSE Top 40
)

# Index friendly names with emoji flags
index_names <- c(
  "^GSPC" = "🇺🇸 S&P 500", 
  "^NDX" = "🇺🇸 Nasdaq 100", 
  "^STOXX50E" = "🇪🇺 EURO STOXX 50", 
  "^FTSE" = "🇬🇧 FTSE 100", 
  "^GDAXI" = "🇩🇪 DAX", 
  "^FCHI" = "🇫🇷 CAC 40",
  "^OMXSPI" = "🇸🇪 OMX Stockholm", 
  "^OMXC25" = "🇩🇰 OMX Copenhagen", 
  "^OMXHPI" = "🇫🇮 OMX Helsinki", 
  "OSEBX.OL" = "🇳🇴 Oslo OBX",
  "^N225" = "🇯🇵 Nikkei 225", 
  "^HSI" = "🇭🇰 Hang Seng", 
  "000300.SS" = "🇨🇳 CSI 300", 
  "^KS11" = "🇰🇷 KOSPI", 
  "^NSEI" = "🇮🇳 Nifty 50", 
  "^BVSP" = "🇧🇷 Bovespa", 
  "^MXX" = "🇲🇽 IPC Mexico", 
  "^GSPTSE" = "🇨🇦 S&P/TSX", 
  "^TASI" = "🇸🇦 Tadawul", 
  "^JN0U.JO" = "🇿🇦 JSE Top 40"
)

# Track which indices successfully loaded
successful_indices <- character(0)

# Process indices safely
market_data <- tibble()

for(region_name in names(market_indices)) {
  for(symbol in market_indices[[region_name]]) {
    # Get data with error handling
    index_data <- tryCatch({
      get_market_data(symbol, start_date, end_date)
    }, error = function(e) NULL)
    
    # Add to dataset if successful (has enough data points)
    if(!is.null(index_data) && nrow(index_data) > 100) {
      index_data <- index_data %>%
        mutate(
          region = region_name,
          index_name = index_names[symbol]
        )
      
      market_data <- bind_rows(market_data, index_data)
      
      # Track successful indices
      successful_indices <- c(successful_indices, index_names[symbol])
    }
  }
}

# Process data for analysis
if(nrow(market_data) > 0) {
  market_data <- market_data %>%
    # Calculate returns
    arrange(symbol, date) %>%
    group_by(symbol) %>%
    mutate(
      # Use adjusted prices if available, otherwise close
      price_col = if("adjusted" %in% names(.)) adjusted else close,
      daily_return = (price_col / lag(price_col) - 1) * 100
    ) %>%
    filter(!is.na(daily_return)) %>%
    # Extract weekday
    mutate(
      weekday = wday(date, label = TRUE),
      year = year(date)
    ) %>%
    # Remove extreme outliers (> 3 standard deviations)
    group_by(symbol) %>%
    mutate(
      return_zscore = abs(scale(daily_return)),
      outlier = return_zscore > 3
    ) %>%
    filter(!outlier) %>%
    select(-outlier, -return_zscore, -price_col) %>%
    ungroup()
}

# Show data summary
num_indices <- n_distinct(market_data$symbol)
num_days <- n_distinct(market_data$date)
date_range <- range(market_data$date)
```

### Global Patterns: Is There a "Best Day" for Markets?

The chart below shows average returns by weekday across all global markets. Green bars show better performance, while red bars show weaker days.

```{r global-weekday-returns}
# Define red-to-green color gradient for performance
performance_colors <- c("#FF4136", "#FF851B", "#FFDC00", "#A3D15C", "#2ECC40")

# Calculate global weekday statistics
global_weekday_stats <- market_data %>%
  group_by(weekday) %>%
  summarize(
    mean_return = mean(daily_return, na.rm = TRUE),
    median_return = median(daily_return, na.rm = TRUE),
    volatility = sd(daily_return, na.rm = TRUE),
    positive_days = sum(daily_return > 0, na.rm = TRUE),
    total_days = n(),
    pct_positive = positive_days / total_days * 100,
    .groups = "drop"
  ) %>%
  mutate(weekday = factor(weekday, levels = c("Mon", "Tue", "Wed", "Thu", "Fri")))

# Find best and worst weekdays
best_weekday <- global_weekday_stats$weekday[which.max(global_weekday_stats$mean_return)]
worst_weekday <- global_weekday_stats$weekday[which.min(global_weekday_stats$mean_return)]

# Assign day-specific emojis
weekday_emojis <- c("Mon" = "😴", "Tue" = "🚀", "Wed" = "📈", "Thu" = "💼", "Fri" = "🎉")

# Map returns to color gradient (red to green)
weekday_colors <- colorRamp(performance_colors)(
  scales::rescale(global_weekday_stats$mean_return)
) %>% rgb(maxColorValue = 255)

# Create custom hover template with emojis
hover_template <- lapply(1:nrow(global_weekday_stats), function(i) {
  day <- global_weekday_stats$weekday[i]
  emoji <- weekday_emojis[as.character(day)]
  paste0(
    "<b>", emoji, " ", day, "</b><br>",
    "Average Return: ", round(global_weekday_stats$mean_return[i], 2), "%<br>",
    "Positive Days: ", round(global_weekday_stats$pct_positive[i], 1), "% of the time<br>",
    "<extra></extra>"
  )
})

# Create enhanced global chart
plot_ly(
  data = global_weekday_stats,
  x = ~weekday,
  y = ~mean_return,
  type = "bar",
  text = ~paste0(weekday_emojis[as.character(weekday)], " ", weekday),
  textposition = "none",
  marker = list(
    color = weekday_colors,
    line = list(color = "#333333", width = 1.5)
  ),
  hovertemplate = unlist(hover_template)
) %>%
  layout(
    title = list(
      text = "Global Weekday Returns 🌎",
      font = list(size = 24)
    ),
    xaxis = list(
      title = "",
      tickfont = list(size = 16)
    ),
    yaxis = list(
      title = "Average Daily Return (%)",
      titlefont = list(size = 16),
      tickfont = list(size = 14)
    ),
    annotations = list(
      list(
        x = best_weekday,
        y = global_weekday_stats$mean_return[global_weekday_stats$weekday == best_weekday],
        text = paste0("⭐ Best Day ⭐<br>", round(global_weekday_stats$mean_return[global_weekday_stats$weekday == best_weekday], 2), "%"),
        showarrow = TRUE,
        arrowhead = 2,
        arrowsize = 1,
        arrowwidth = 2,
        arrowcolor = "#25A75E",
        ax = 0,
        ay = -40,
        bgcolor = "#25A75E",
        bordercolor = "#25A75E",
        borderwidth = 2,
        borderpad = 4,
        font = list(color = "white", size = 12)
      ),
      list(
        x = worst_weekday,
        y = global_weekday_stats$mean_return[global_weekday_stats$weekday == worst_weekday],
        text = paste0("⚠️ Worst Day ⚠️<br>", round(global_weekday_stats$mean_return[global_weekday_stats$weekday == worst_weekday], 2), "%"),
        showarrow = TRUE,
        arrowhead = 2,
        arrowsize = 1,
        arrowwidth = 2,
        arrowcolor = "#d9534f",
        ax = 0,
        ay = 40,
        bgcolor = "#d9534f",
        bordercolor = "#d9534f",
        borderwidth = 2,
        borderpad = 4,
        font = list(color = "white", size = 12)
      )
    ),
    margin = list(t = 100, b = 80, l = 80, r = 80),
    plot_bgcolor = '#f8f9fa',
    paper_bgcolor = '#f8f9fa'
  )
```

*Markets included in this analysis: `r paste(sort(successful_indices), collapse=", ")`*

### Check Your Market's Pattern

Different markets can show different patterns. Click on any flag to see its specific weekday performance:

```{r market-specific-analysis}
# Filter to only include successfully loaded indices
market_data_filtered <- market_data %>%
  filter(index_name %in% successful_indices)

# Calculate statistics for each index by weekday
index_weekday_stats <- market_data_filtered %>%
  group_by(region, symbol, index_name, weekday) %>%
  summarize(
    mean_return = mean(daily_return, na.rm = TRUE),
    median_return = median(daily_return, na.rm = TRUE),
    volatility = sd(daily_return, na.rm = TRUE),
    positive_days = sum(daily_return > 0, na.rm = TRUE),
    total_days = n(),
    pct_positive = positive_days / total_days * 100,
    .groups = "drop"
  ) %>%
  mutate(weekday = factor(weekday, levels = c("Mon", "Tue", "Wed", "Thu", "Fri")))

# Get unique indices that have data
available_indices <- unique(index_weekday_stats$index_name)

# Extract the flag emoji from each index name
flags <- sapply(available_indices, function(idx) {
  # Extract the flag emoji at the beginning of the string
  flag <- stringr::str_extract(idx, "^[\\p{So}]+")
  # If no emoji is found, use a default
  if(is.na(flag)) flag <- "🏳️"
  return(flag)
})

# Create buttons for the flag selector
flag_buttons <- lapply(seq_along(available_indices), function(i) {
  idx <- available_indices[i]
  flag <- flags[i]
  
  # Filter data for this index
  idx_data <- index_weekday_stats %>%
    filter(index_name == idx)
  
  # Find best and worst days
  best_day <- idx_data$weekday[which.max(idx_data$mean_return)]
  best_return <- max(idx_data$mean_return)
  worst_day <- idx_data$weekday[which.min(idx_data$mean_return)]
  worst_return <- min(idx_data$mean_return)
  
  # Create color mapping
  bar_colors <- colorRamp(performance_colors)(
    scales::rescale(idx_data$mean_return)
  ) %>% rgb(maxColorValue = 255)
  
  # Create button with flag as the label
  list(
    method = "update",
    args = list(
      # Trace update
      list(
        x = list(idx_data$weekday),
        y = list(idx_data$mean_return),
        marker = list(color = bar_colors),
        customdata = list(cbind(
          idx_data$pct_positive
        ))
      ),
      # Layout update
      list(
        title = list(
          text = paste0("Weekday Returns: ", idx, " 📈"),
          font = list(size = 24)
        ),
        annotations = list(
          list(
            x = best_day,
            y = best_return,
            text = paste0("⭐ Best Day ⭐<br>", round(best_return, 2), "%"),
            showarrow = TRUE,
            arrowhead = 2,
            arrowsize = 1,
            arrowwidth = 2,
            arrowcolor = "#25A75E",
            ax = 0,
            ay = -40,
            bgcolor = "#25A75E",
            bordercolor = "#25A75E",
            borderwidth = 2,
            borderpad = 4,
            font = list(color = "white", size = 12)
          ),
          list(
            x = worst_day,
            y = worst_return,
            text = paste0("⚠️ Worst Day ⚠️<br>", round(worst_return, 2), "%"),
            showarrow = TRUE,
            arrowhead = 2,
            arrowsize = 1,
            arrowwidth = 2,
            arrowcolor = "#d9534f",
            ax = 0,
            ay = 40,
            bgcolor = "#d9534f",
            bordercolor = "#d9534f",
            borderwidth = 2,
            borderpad = 4,
            font = list(color = "white", size = 12)
          ),
          list(
            xref = "paper",
            yref = "paper",
            x = 0.5,
            y = -0.15,
            text = paste("Currently showing:", idx),
            showarrow = FALSE,
            font = list(size = 14)
          )
        )
      )
    ),
    label = flag,
    args2 = list(
      # Secondary trigger to update title below the chart
      list(),
      list(
        annotations = list(
          list(
            x = best_day,
            y = best_return,
            text = paste0("⭐ Best Day ⭐<br>", round(best_return, 2), "%"),
            showarrow = TRUE,
            arrowhead = 2,
            arrowsize = 1,
            arrowwidth = 2,
            arrowcolor = "#25A75E",
            ax = 0,
            ay = -40,
            bgcolor = "#25A75E",
            bordercolor = "#25A75E",
            borderwidth = 2,
            borderpad = 4,
            font = list(color = "white", size = 12)
          ),
          list(
            x = worst_day,
            y = worst_return,
            text = paste0("⚠️ Worst Day ⚠️<br>", round(worst_return, 2), "%"),
            showarrow = TRUE,
            arrowhead = 2,
            arrowsize = 1,
            arrowwidth = 2,
            arrowcolor = "#d9534f",
            ax = 0,
            ay = 40,
            bgcolor = "#d9534f",
            bordercolor = "#d9534f",
            borderwidth = 2,
            borderpad = 4,
            font = list(color = "white", size = 12)
          ),
          list(
            xref = "paper",
            yref = "paper",
            x = 0.5,
            y = -0.15,
            text = paste("Currently showing:", idx),
            showarrow = FALSE,
            font = list(size = 14)
          )
        )
      )
    )
  )
})

# Get first index data for initial plot
first_idx <- available_indices[1]
first_idx_data <- index_weekday_stats %>%
  filter(index_name == first_idx)

# Find best and worst days for first index
first_best_day <- first_idx_data$weekday[which.max(first_idx_data$mean_return)]
first_best_return <- max(first_idx_data$mean_return)
first_worst_day <- first_idx_data$weekday[which.min(first_idx_data$mean_return)]
first_worst_return <- min(first_idx_data$mean_return)

# Create color mapping for first index
first_bar_colors <- colorRamp(performance_colors)(
  scales::rescale(first_idx_data$mean_return)
) %>% rgb(maxColorValue = 255)

# Create plot with flag buttons
plot_ly(
  data = first_idx_data,
  x = ~weekday,
  y = ~mean_return,
  type = "bar",
  text = ~paste0(weekday_emojis[as.character(weekday)], " ", weekday),
  textposition = "none",
  marker = list(
    color = first_bar_colors,
    line = list(color = "#333333", width = 1.5)
  ),
  hovertemplate = paste(
    "<b>%{text}</b><br>",
    "Average Return: %{y:.2f}%<br>",
    "Positive Days: %{customdata[0]:.1f}% of the time<br>",
    "<extra></extra>"
  ),
  # This contains additional data for each bar that's used in the hover template
  customdata = cbind(
    first_idx_data$pct_positive
  )
) %>%
  layout(
    title = list(
      text = paste0("Weekday Returns: ", first_idx, " 📈"),
      font = list(size = 24)
    ),
    xaxis = list(
      title = "",
      tickfont = list(size = 16)
    ),
    yaxis = list(
      title = "Average Daily Return (%)",
      titlefont = list(size = 16),
      tickfont = list(size = 14),
      zeroline = TRUE,
      zerolinecolor = '#ddd',
      zerolinewidth = 1
    ),
    updatemenus = list(
      list(
        buttons = flag_buttons,
        type = "buttons",
        direction = "right",
        xanchor = "center",
        yanchor = "top",
        x = 0.5,
        y = 1.15,
        font = list(size = 24), # Larger font for flags
        padding = list(t = 5, b = 5),
        borderwidth = 0,
        showactive = TRUE
      )
    ),
    annotations = list(
      list(
        x = first_best_day,
        y = first_best_return,
        text = paste0("⭐ Best Day ⭐<br>", round(first_best_return, 2), "%"),
        showarrow = TRUE,
        arrowhead = 2,
        arrowsize = 1,
        arrowwidth = 2,
        arrowcolor = "#25A75E",
        ax = 0,
        ay = -40,
        bgcolor = "#25A75E",
        bordercolor = "#25A75E",
        borderwidth = 2,
        borderpad = 4,
        font = list(color = "white", size = 12)
      ),
      list(
        x = first_worst_day,
        y = first_worst_return,
        text = paste0("⚠️ Worst Day ⚠️<br>", round(first_worst_return, 2), "%"),
        showarrow = TRUE,
        arrowhead = 2,
        arrowsize = 1,
        arrowwidth = 2,
        arrowcolor = "#d9534f",
        ax = 0,
        ay = 40,
        bgcolor = "#d9534f",
        bordercolor = "#d9534f",
        borderwidth = 2,
        borderpad = 4,
        font = list(color = "white", size = 12)
      ),
      list(
        xref = "paper",
        yref = "paper",
        x = 0.5,
        y = -0.15,
        text = paste("Currently showing:", first_idx),
        showarrow = FALSE,
        font = list(size = 14)
      )
    ),
    margin = list(t = 100, b = 100, l = 80, r = 80),
    plot_bgcolor = '#f8f9fa',
    paper_bgcolor = '#f8f9fa',
    showlegend = FALSE
  )
```
